% Fiverr/Upwork-optimized resume variant
% Service-oriented, outcome-first, keyword-optimized for marketplace buyers
\documentclass[10.5pt]{res} 

\usepackage[hmargin=.5cm,vmargin=1.1cm]{geometry}
\usepackage{enumitem}
\usepackage{fdsymbol}
\usepackage{graphicx}
\graphicspath{{./}}

\usepackage[most]{tcolorbox}

\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\textwidth=6.9in
\begin{document} 
\name{\centering \Huge Jason St George}
{\fontsize{10.5}{6}\selectfont
\centering 
\href{mailto:jason@jasonstgeorge.com}{jason@jasonstgeorge.com} \hspace{.15 cm} $\vert$ \hspace{.15 cm} \href{https://github.com/ifrit98}{github.com/ifrit98} \hspace{.15 cm} $\vert$ \hspace{.15 cm} \href{https://linkedin.com/in/stgeorgejas}{linkedin.com/in/stgeorgejas} \hspace{.15 cm} $\vert$ \hspace{.15 cm} \href{https://jasonstgeorge.com}{jasonstgeorge.com}\\


\hrulefill
}
\vspace{0.25cm}

\begin{resume}
\begin{center}
{\large \textbf{Senior AI / ML Systems Engineer --- Production Infrastructure, Agentic Systems, LLM Integration, Real-Time Inference}}
\end{center}
\vspace{-0.15cm}

{\bf What I Deliver} \vspace{.27 cm}\\
Senior engineer with 7+ years shipping production AI and backend systems---from distributed LLM training and real-time edge inference to scalable API services and workflow automation. Trusted in high-security, mission-critical environments; now offering the same rigor, speed, and documentation quality to startups and SMBs.
\vspace{.27 cm}
\begin{itemize}
    \item Build and deploy \textbf{AI agents/chatbots} integrated with business tools (CRM, docs, support, Slack, email) using OpenAI/Anthropic APIs, tool-calling, and RAG pipelines.
    \item Deliver \textbf{production backend services} (FastAPI, auth, DB, Docker/k8s) with monitoring, tests, and handoff documentation so your team can maintain everything.
    \item \textbf{Optimize ML systems}---latency, cost, throughput, GPU utilization---with profiling, before/after metrics, and a written report.
    \item \textbf{Automate workflows}: API integrations, data pipelines, Zapier/Make + custom Python, scheduled jobs, and notification hooks.
\end{itemize}

{\bf Service Offerings} \\
\begin{itemize}
    \item \textbf{AI Chatbot / Agent Implementation} --- Custom agents using OpenAI/Anthropic stack with tool integrations, retrieval-augmented generation (RAG), memory, and deployment. Integrated with your existing tools and APIs.
    \item \textbf{FastAPI Microservice (Production-Ready)} --- Endpoints, validation, database models/migrations, auth, test suite, Dockerized deployment, and handoff documentation. Ready to ship.
    \item \textbf{Workflow Automation} --- Connect your systems: API integrations, data pipelines, scheduled processing, Zapier/Make + custom Python when off-the-shelf falls short.
    \item \textbf{PyTorch / ML Performance Optimization} --- Profiling, bottleneck identification, code-level fixes (mixed precision, dataloader tuning, memory management, multi-GPU). Delivered with before/after benchmarks.
    \item \textbf{Docker + Kubernetes Deployment} --- Containerize your app, set up Helm charts, autoscaling, rollout strategy, monitoring hooks, and CI/CD pipeline. Runs anywhere.
    \item \textbf{AI Architecture Review + Roadmap} --- Evaluate your current system, identify scaling bottlenecks, and deliver an implementation roadmap with prioritized next steps.
\end{itemize}

{\bf Proof Points (Selected Wins)} \\
\begin{itemize}
    \item \textbf{Decentralized Storage Network} --- Built and operated a production storage platform from the ground up: anti-tamper verification, reliability/integrity guarantees, incentive system design, and real-time monitoring. Operated to \textbf{\textasciitilde\$7M avg MRR (\textasciitilde\$60M revenue)}.\\
    \textit{Transferable:} production system design under adversarial conditions, reliability engineering, API-driven distributed infrastructure.

    \item \textbf{U.S.\ Navy (high-security; details available where permissible)} --- Led ML engineering for a real-time detection pipeline: signal processing + deep learning, optimizing accuracy/false-alarm tradeoffs and latency. Built simulation + synthetic-data workflows for robust training. Helped secure \textbf{\textasciitilde\$5M multi-year follow-on}.\\
    \textit{Transferable:} low-latency AI inference pipelines, noisy-signal classification, edge deployment under strict performance constraints.

    \item \textbf{Production LLM Fine-Tuning (128-GPU)} --- Owned end-to-end: data pipelines, training orchestration, deployment, and operator workflows in regulated environments. Reduced fine-tuning costs \textbf{65\%} via quantized adapters on commodity hardware.\\
    \textit{Transferable:} LLM customization, cost-efficient training, model deployment for teams without ML infra experience.

    \item \textbf{Real-Time Edge Inference} --- Built DSP$\rightarrow$deep learning pipeline achieving \textbf{$<$50\,ms} end-to-end latency on embedded devices. Shipped to production.\\
    \textit{Transferable:} real-time inspection, IoT sensor AI, on-device inference for latency-sensitive applications.

    \item \textbf{AfterFiat (\href{https://afterfiat.xyz}{afterfiat.xyz})} --- Published long-form systems thesis on trust, verification, and resilient infrastructure for the AI era.\\
    \textit{Transferable:} systems thinking, architecture documentation, technical writing at publication quality.
\end{itemize}

{\bf Work Experience} \vspace{0.27 cm} \\
{\bf Senior Machine Learning Software Engineer} \hfill July 2020 -- Present\\
Black River Systems Co., Utica, NY \\
\begin{itemize}\rightmargin=0cm \itemsep 2pt
    \item Owned distributed LLM fine-tuning capability end-to-end (data pipeline $\rightarrow$ training $\rightarrow$ deployment $\rightarrow$ operator workflows) in high-security production environment.
    \item Built low-latency edge inference pipeline ($<$50\,ms E2E on Jetson)---transferable to real-time inspection, IoT, and sensor AI applications.
    \item Shipped online learning system for autonomous fleets with bandwidth-aware sync; reduced data egress \textbf{60\%} while maintaining model quality.
    \item Designed scalable agentic system with continuous data ingestion and Blue-Green deployment infrastructure.
    \item Led stakeholder communication and technical briefings; influenced annual AI readiness budget decisions.
    \item Mentored junior engineers on real-time object detection (YOLO) and embedded deployment.
\end{itemize}

{\bf Data Scientist I} \hfill June 2019 -- May 2020\\
Northeast Information Discovery, Inc., Canastota, NY \\
\begin{itemize}\rightmargin=0cm \itemsep 2pt
    \item Built RF signal classifier (+12pp accuracy) using attention-based spectral encoders---applicable to any noisy-signal classification task.
    \item Developed production APIs and deployed models into streaming environments (R, Python, C++).
\end{itemize}

{\bf Teaching Assistant (Advanced OOP)} \hfill August 2018 -- January 2019\\
Rochester Institute of Technology, Rochester, NY \\
\begin{itemize}\rightmargin=0cm \itemsep 2pt
    \item Redesigned course recitations around test-driven patterns; improved student project quality 25\%.
\end{itemize}

{\bf Selected Public Work (Client-Relevant)} \\

\textbf{\href{https://afterfiat.xyz}{AfterFiat}} --- Long-form systems thesis and applied architecture for trust, verification, and resilient AI-era infrastructure.\\
\textit{Proves:} systems thinking, architecture documentation, rigorous technical writing.\\[0.15cm]
\textbf{\href{https://github.com/ifrit98/mlcurves}{mlcurves}} --- Lightweight Python module for generating and analyzing ML training curves.\\
\textit{Proves:} clean Python packaging, developer tooling, ML workflow understanding.\\[0.15cm]
\textbf{\href{https://github.com/ifrit98/begnaliai}{Bengali.ai Grapheme Classification}} --- End-to-end deep learning pipeline with augmentation and model optimization.\\
\textit{Proves:} full ML pipeline delivery (data $\rightarrow$ training $\rightarrow$ evaluation), production-quality code.
\vspace{.27 cm}

{\bf Publications} \\
\href{https://drive.google.com/file/d/1Xps3u00zFacalEtLFYzkAAy0NfmRkHLB/view?usp=sharing}{Music Style Transformer} --- \textit{ICAI/WorldComp} (2019)\\[0.1cm]
\href{https://drive.google.com/file/d/1pdxPst1CBMQQrgR2OGiBcKQgI_Hzg6gX/view?usp=sharing}{Sonification of Simulated Black Hole Merger Data} --- \textit{MSV} (2018)
\vspace{.27 cm}

{\bf Education} \\
\textbf{M.S., Computer Science} --- Rochester Institute of Technology \hfill May 2019\\
Focus: Deep Learning, Statistical Machine Learning, Advanced ML Topics\\[0.15cm]
\textbf{B.M., Performance (Music Theory Minor)} --- University of North Texas \hfill May 2013
\vspace{.27 cm}

{\bf Toolchain} \\
\begin{itemize}
    \item \textbf{Languages:} Python, Rust, R, Bash, SQL (plus C++/JS/TS familiarity)
    \item \textbf{Frameworks/Infra:} PyTorch, TensorFlow, NumPy/SciPy, Pandas, FastAPI, Docker, Kubernetes, Slurm, Git, Linux/Unix, AWS/GCP/Azure
\end{itemize}

{\bf Marketplace Keywords} \\
{\small AI chatbot development, AI agent development, workflow automation, FastAPI developer, Python API development, PyTorch optimization, Docker, Kubernetes, MLOps, LLM integration, RAG, model deployment, inference optimization, production debugging, CI/CD, microservices, GPU training, distributed systems, backend engineering, technical writing}

\end{resume} 
\end{document}
